Mreže

### 2016-05-04 article.tex
Dodal slike za primere mrez, closes #1

>>>>

\pagebreak
\section{Literatura}
\begin{itemize}
\item dodaj Cohena
\item dodaj Vidava
\item Predavanja iz algebraične kombinatorike dostopna na \url{http://www.math.cornell.edu/~levine/18.312/}
\item \url{https://en.wikipedia.org/wiki/Partially_ordered_set}
\item \url{https://en.wikipedia.org/wiki/Lattice_\%28order\%29}
\item \url{https://en.wikipedia.org/wiki/Modular_lattice}
\item \url{https://en.wikipedia.org/wiki/Distributive_lattice}đ
\item \url{http://www-rohan.sdsu.edu/~gawron/mathling/course_core/lectures/posets_slides.pdf}
\item \url{http://www.math.hawaii.edu/~jb/math618/os9uh.pdf}

\end{itemize}
